Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-21 paper/tex/sections/results.tex
add new galaxy plot

\todo{There will also be a little bit more text to explain the example distribution over galaxies in the lower panel -- will make properly once Floor combines the latest fiducial simulation data (this plot is sampling uniformly rather than based on the distribution)}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{sources_on_mw.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity. The large $\odot$ shows the position of the Sun. Stars represent a typical example of the detectable systems in a 4-year LISA mission. \todo{make proper plot, maybe separate panels for different types (hard to arange then though), thoughts on black background?}}
    \label{fig:detectable_distance_dist}
\end{figure}

>>>>

In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy. We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun. Yet we also show that systems are detectable out to the edges of the galaxy and this is especially true for NSNSs.

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights. The coloured lines show the 90\% contour for each of the individual DCO types. The `x' shows the centre of the galaxy, whilst the $\odot$ shows the position of the Sun.}
    \label{fig:detectable_distance_dist}
\end{figure}
